Sensitivity Analysis

### 2024-10-10 Sections/Saturation.tex
10.10

>>>>

	\subsubsection{Empirical correlations}

	The empirical correlations for $D_i$ and $\Upsilon$ were derived by {\color{red}article 1} and validated for temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s. Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables. The region marked with the white dashed line represents the confidence region, where the model has been tested. Both correlations should be equal of greater than zero, to avoid unphysical behaviour such as the reverse mass transfer. The multiple linear regression functions are combined with the rectifier function to ensure the non-negativity.

	\begin{figure}[!ht]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Di.png}
		\caption{Multiple linear regression $D_i^R = f(Re, F)$}
		\label{fig:Correlation_Di}
	\end{figure}

	\begin{figure}[!ht]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Gamma.png}
		\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
		\label{fig:Correlation_Gamma}
	\end{figure}
